Making Sequential Programs Deterministic

### 2019-04-04 experiments.tex
deflaker todo

\section{Comparison to Deflaker}
Deflaker~\cite{deflaker}, like NonDex, reports tests that could be flaky. Ideally, we would have 
liked to run all three tools (NonDex, DeFlaker, and \TheDeterminismChecker) on an open source project
that wasn't explored by any of the tool for a fair comparison. Unfortunately, there are issues with the
DeFlaker plugin and we weren't able to run it on any project. We have created a Github issue for the same
in its repository.
\todo{Deflaker works now. Tried on retrofit: only works where there is sufficient change in code coverage between head and its parent.
Looked throught= about 10 commits, didn't find differential code coverage and therefore no flakes}
\todo{Deflaker requires maven build. Randoop is on gradle.}

>>>>

\section{Comparison to Deflaker}
Deflaker~\cite{deflaker}, like NonDex, reports tests that could be flaky. 
While we would have like to run DeFlaker on Randoop for a fair comparison of the tools,
we were unable to do so because Deflaker works with projects built with maven and Randoop
uses gradle for its build system. We plan to convert Randoop's build system to maven and 
perform this case study.
%Ideally, we would have 
%liked to run all three tools (NonDex, DeFlaker, and \TheDeterminismChecker) on an open source project
%that wasn't explored by any of the tool for a fair comparison. Unfortunately, there are issues with the
%DeFlaker plugin and we weren't able to run it on any project. We have created a Github issue for the same
%in its repository.
%\todo{Deflaker works now. Tried on retrofit: only works where there is sufficient change in code coverage between head and its parent.
%Looked throught= about 10 commits, didn't find differential code coverage and therefore no flakes}
%\todo{Deflaker requires maven build. Randoop is on gradle.}
